EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-06 draft.tex
Some comments here and there. Please @mariosky check them out

\section{Container-based application} 
\label{docker}

@@

We present the results of the experiments in this section.
% The effect of a
% different number of populations on execution time is reported in  Section
% \ref{sec:exp1results}.
% The results of the performance comparison between homogeneous and
% heterogeneous search strategies are presented in Section \ref{sec:exp2results}.     
%

@@

\begin{table}[]
    \small
    \caption{ Median of evaluation rate per second, for each number of workers and dimension}
    \label{tab:medians}
    \vspace{0.25cm}
    \centering

@@

\begin{table}[]
    \small
    \caption{ Speedup of incrementing the number of workers for each dimension showing the p-rate for the Wilcoxon test}
    \label{tab:medians}
    \vspace{0.25cm}
    \centering
    \begin{tabular}{lllllll}
              &               &               & \multicolumn{2}{l}{5 Populations} & \multicolumn{2}{l}{10 Populations} \\
    Dimension & \multicolumn{2}{l}{Increment} & Speedup         & p-value         & Speedup          & p-value         \\
    2         & 1w            & 2w            & 1.94            & 6E-16           & 1.84             & 2E-16           \\
              & 2w            & 4w            & 1.61            & 2E-15           & 1.83             & 1E-15           \\
              & 4w            & 8w            & 1.24            & 1E-06           & 1.77             & 2E-16           \\
    3         & 1w            & 2w            & 1.93            & 2E-16           & 1.90             & 2E-16           \\
              & 2w            & 4w            & 1.44            & 8E-15           & 1.71             & 2E-16           \\
              & 4w            & 8w            & 1.14            & 3E-05           & 1.83             & 2E-16           \\
    5         & 1w            & 2w            & 1.91            & 9E-16           & 1.91             & 2E-16           \\
              & 2w            & 4w            & 1.52            & 3E-11           & 1.82             & 2E-16           \\
              & 4w            & 8w            & 1.06            & 5E-03           & 1.77             & 2E-16           \\
    10        & 1w            & 2w            & 1.92            & 3E-16           & 1.90             & 2E-16           \\
              & 2w            & 4w            & 1.58            & 3E-16           & 1.89             & 2E-16           \\
              & 4w            & 8w            & 1.09            & 1E-03           & 1.78             & 2E-16           \\
    20        & 1w            & 2w            & 1.91            & 2E-16           & 1.89             & 2E-16           \\
              & 2w            & 4w            & 1.64            & 2E-15           & 1.97             & 2E-16           \\
              & 4w            & 8w            & 1.04            & 1E-02           & 1.80             & 2E-16           \\
    40        & 1w            & 2w            & 2.00            & 2E-16           & 1.95             & 2E-16           \\
              & 2w            & 4w            & 1.46            & 1E-09           & 1.95             & 2E-16           \\
              & 4w            & 8w            & 1.07            & 3E-02           & 1.98             & 2E-16          
    \end{tabular}
    \end{table}

\begin{figure}[h!p]
    \centering
    \includegraphics[width=\textwidth]{evalrate}
    \caption{Rate of number of evaluations per second, for 30 instances of the function, with different number of workers and populations sizes }
    \label{fig:spworker}
\end{figure}

\begin{figure}[h!p]
    \centering
    \includegraphics[width=\textwidth]{evalsworker}
    \caption{Total number of evaluations for 30 instances of the function, with different number of workers and populations sizes }
    \label{fig:spworker}
\end{figure}

@@

% This is only an idea of the section
%
% First you have to say that cloud is a way of describing deployment to any kind of infrastructure in a reproducible way, and it needn't be in the cloud proper, it can be deployed to anything, that's precisely the thing. 
Several options:
    A virtual machine with a container-optimized operating system, for example,
     Google Compute Engine VMs, or Amazon EC2.  We still need to provision the
      virtual machine and run docker-compose commands as we would do in a local 
      workstation. % Remember that Salza et al. used CoreOS, which is optimized for containers - JJ

>>>>

% Maybe these three sections should be merged; they are all experimental set up and the two next ones start with "experimental"
% (and he next one too) - JJ
\section{Container-based application} 
\label{docker}

@@

We present the results of the experiments in this section. % that's pretty obvious. Say what you intend to prove with the experiments and why - JJ
% The effect of a
% different number of populations on execution time is reported in  Section
% \ref{sec:exp1results}.
% The results of the performance comparison between homogeneous and
% heterogeneous search strategies are presented in Section \ref{sec:exp2results}.     
%

@@

\begin{table}[h!tbp]
    \small
    \caption{Median evaluation rate per second, for each number of workers and dimension}
        % mark significant differences in some way - JJ

    \label{tab:medians}
    \vspace{0.25cm}
    \centering

@@

\begin{table}[]
    \small
    \caption{Speedup achieved with incrementing the number of workers for each dimension showing the p-rate for the Wilcoxon test}
    % mark significant differences in some way - JJ
    \label{tab:medians}
    \vspace{0.25cm}
    \centering
    \begin{tabular}{lllllll}
              &               &               & \multicolumn{2}{l}{5 Populations} & \multicolumn{2}{l}{10 Populations} \\
    Dimension & \multicolumn{2}{l}{Increment} & Speedup         & p-value         & Speedup          & p-value         \\
    2         & 1w            & 2w            & 1.94            & 6E-16           & 1.84             & 2E-16           \\
              & 2w            & 4w            & 1.61            & 2E-15           & 1.83             & 1E-15           \\
              & 4w            & 8w            & 1.24            & 1E-06           & 1.77             & 2E-16           \\
    3         & 1w            & 2w            & 1.93            & 2E-16           & 1.90             & 2E-16           \\
              & 2w            & 4w            & 1.44            & 8E-15           & 1.71             & 2E-16           \\
              & 4w            & 8w            & 1.14            & 3E-05           & 1.83             & 2E-16           \\
    5         & 1w            & 2w            & 1.91            & 9E-16           & 1.91             & 2E-16           \\
              & 2w            & 4w            & 1.52            & 3E-11           & 1.82             & 2E-16           \\
              & 4w            & 8w            & 1.06            & 5E-03           & 1.77             & 2E-16           \\
    10        & 1w            & 2w            & 1.92            & 3E-16           & 1.90             & 2E-16           \\
              & 2w            & 4w            & 1.58            & 3E-16           & 1.89             & 2E-16           \\
              & 4w            & 8w            & 1.09            & 1E-03           & 1.78             & 2E-16           \\
    20        & 1w            & 2w            & 1.91            & 2E-16           & 1.89             & 2E-16           \\
              & 2w            & 4w            & 1.64            & 2E-15           & 1.97             & 2E-16           \\
              & 4w            & 8w            & 1.04            & 1E-02           & 1.80             & 2E-16           \\
    40        & 1w            & 2w            & 2.00            & 2E-16           & 1.95             & 2E-16           \\
              & 2w            & 4w            & 1.46            & 1E-09           & 1.95             & 2E-16           \\
              & 4w            & 8w            & 1.07            & 3E-02           & 1.98             & 2E-16          
    \end{tabular}
    \end{table}

\begin{figure}[h!p]
    \centering
    \includegraphics[width=\textwidth]{evalrate}
    \caption{Boxplot of the number of evaluations per second, for 30 instances of the function, with different number of workers and populations sizes }
    \label{fig:spworker}
\end{figure}

\begin{figure}[h!p]
    \centering
    \includegraphics[width=\textwidth]{evalsworker}
    \caption{Boxplot of the total number of evaluations for 30 instances of the function, with different number of workers and populations sizes }
    % Which function? - JJ
    \label{fig:spworker}
\end{figure}

@@

% This is only an idea of the section
%
% First you have to say that cloud is a way of describing deployment to any kind of infrastructure in a reproducible way, and it needn't be in the cloud proper, it can be deployed to anything, that's precisely the thing. But make clear that when you use a cloud provider, there are more options to do it... - JJ
Several options:
    A virtual machine with a container-optimized operating system, for example,
     Google Compute Engine VMs, or Amazon EC2.  We still need to provision the
      virtual machine and run docker-compose commands as we would do in a local 
      workstation. % Remember that Salza et al. used CoreOS, which is optimized for containers - JJ
